Unshuffling Permutations

### 2015-06-27 article.tex
reduction

@@

\author{%
  Samuele Giraudo\inst{1} \and
  St\'ephane Vialette\inst{1}
}% end author
\institute{%
  Universit\'e Paris-Est, LIGM (UMR 8049), CNRS, UPEM, ESIEE Paris, ENPC, 
  F-77454, Marne-la-Vallée, France\\
  \email{vialette@univ-mlv.fr}
}% end institute
\date{\today}

@@

\begin{proposition}
Let $\pi \in S_{2n}$.
Then,
$\pi$ is the union of two order-isomorphic pattern 
if and only if
there exists a perfect containment-free mathing
$\mathcal{M}$ of $G_\pi$ such that
\end{proposition}

>>>>

\DeclareMathOperator{\LEFT}{\ell}
\DeclareMathOperator{\RIGHT}{r}

@@

\author{%
  Samuele Giraudo\inst{1} \and
  St\'ephane Vialette\inst{1}
}% end author
\institute{%
  Universit\'e Paris-Est, LIGM (UMR 8049), CNRS, UPEM, ESIEE Paris, ENPC,
  F-77454, Marne-la-Vallée, France\\
  \email{samuele.giraudo@univ-mlv.fr} \\
  \email{vialette@univ-mlv.fr}
}% end institute
\date{\today}

@@

\begin{proposition}
Let $\pi \in S_{2n}$.
Then,
$\pi$ is the union of two order-isomorphic pattern 
if and only if
there exists a perfect containment-free mathing
$\mathcal{M}$ of $G_\pi$ such that
$\LEFT(\mathcal{M}) \simeq \RIGHT(\mathcal{M})$.
\end{proposition}

\begin{proposition}
Deciding whether a permutation is the union of two
order-isomorphic pattern is \NPC.
\end{proposition}

\begin{align*}
N_4 &= 2(2n + k + 2) + 1  = 4n + 2k + 5 \\
N_3 &= 2(2N_4 + 2n + 2k + 4) + 1 = 20n + 12k + 9 \\
N_2 &= 2(2N_3 + 2n + 2k + 4) + 1 \\
N_1 &= 2(2N_2 + 2n + 2k + 4) + 1\text{.}
\end{align*}

\begin{align*}
\sigma'  &= ((k+1) \; \sigma \; (k+2)) \; [2N_2 + N_4 + 2n + k + 2] \\
\pi'     &= ((n+1) \; \pi \; (n+2)) \; [2N_2 + N_4 + n + k + 2] \\
\sigma'' &= \sigma \; [2N_2 + N_4] \\
\pi''    &= \pi \; [2N_2 + N_4 + k] \\
\nu_1    &= \nearrow_{N_1} \; [2N_2 + 2N_3 + 2N_4 + 2n + 2k + 4] \\
\nu'_1   &= \nearrow_{N_1} \; [N_1 + 2N_2 + 2N_3 + 2N_4 + 2n + 2k + 4] \\
\nu_2    &= \nearrow_{N_2} \; [N_2] \\
\nu'_2   &= \searrow_{N_2} \\
\nu_3    &= \nearrow_{N_3} \; [2N_2 + 2N_4 + 2n + 2k + 4] \\
\nu'_3   &= \nearrow_{N_3} \; [2N_2 + N_3 + 2N_4 + 2n + 2k + 4] \\
\nu_4    &= \searrow_{N_4} \; [2N_2 + N_4 + 2n + 2k + 4] \\
\nu'_4   &= \searrow_{N_4} \; [2N_2]
\end{align*}

$$
\mu
=
\nu_1 \; \nu_2 \; \nu'_1 \; \nu_3 \; \sigma' \; \nu_4 \; \nu'_3 \; \pi' \; \nu'_4 \; \pi'' \; \sigma''
$$

\begin{claim}
  \label{claim:no nu_1 - nu_1 edge}
  There is no $(\nu_1, \nu_2)$-edge in $\mathcal{M}$.
\end{claim}

\begin{proof}[of Claim~\ref{claim:no nu_1 - nu_1 edge}]
Suppose, aiming at a contradiction that there exists
a $(\nu_1, \nu_2)$-edge in $\mathcal{M}$.
\begin{tikzpicture}

\end{tikzpicture}
\qed
\end{proof}

\begin{claim}
There is at least one $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
\end{claim}
